Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-24 article.tex
Added current simulation images.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:simulation1}a):
\begin{figure} \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs} and [b] its reconstruction. Color represents
    aerosol density. The density units are $10^{15}~{\rm
      particles}/{\rm cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude \SI{3.3}{\km}, and has horizontal
width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
lateral width of \SI{24}{\km} and vertical thickness of
\SI{2.1}{\km}. Note that the horizontal widths are much larger than
the vertical ones. This is consistent with scales of atmospheric
aerosol distributions.

\noindent{\bf Cameras}: The cameras are created by the MC simulations.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:simulation1}a.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:simulation1}a, while the recovered
3D distribution is visualized in \cref{fig:simulation1}b. The
distributions appear consistent, though there are errors that stem
from the random noise in the images. To quantify the results, we use a
relative error measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
  \hspace{-0.05cm}
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

We created a {\em Haze Front} scene. \cref{fig:simulation2}a shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation2}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of a
    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{15}~{\rm particles}/{\rm
      cm}^3.$}
  \label{fig:simulation2}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:simulation2}b visualizes the recovered
3D distribution of this scene. For the {\em Haze Front},
$\epsilon=0.198$.

>>>>

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:two_clouds_sim}a):
the first is centered at altitude \SI{3.3}{\km}, and has horizontal
width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
lateral width of \SI{24}{\km} and vertical thickness of
\SI{2.1}{\km}. Note that the horizontal widths are much larger than
the vertical ones. This is consistent with scales of atmospheric
aerosol distributions.

\noindent{\bf Cameras}: The cameras are created by the MC simulations.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:two_clouds_sim}a, while the recovered
3D distribution is visualized in \cref{fig:two_clouds_sim}b. The
distributions appear consistent, though there are errors that stem
from the random noise in the images. To quantify the results, we use a
relative error measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

We created a {\em Haze Front} scene. \cref{fig:front_sim}a shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/two_clouds}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs} and [b] its reconstruction. Color represents
    aerosol density. The density units are $10^{6}~{\rm
      particles}/{\rm m}^3.$}
  \label{fig:two_clouds_sim}
\end{figure}
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/front}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of a
    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{6}~{\rm particles}/{\rm
      m}^3.$}
  \label{fig:front_sim}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:front_sim}b visualizes the recovered
3D distribution of this scene. For the {\em Haze Front},
$\epsilon=0.198$.
